Game Theory

### 2021-11-12 code/analysis.Rmd
edits for BoS

#TODO
- for less munging, put player role into round
- put players increment into record!
# Pre-process

@@

# Metrics
Welp, people definitely took the "click through" approach ...

@@

@@

```{r}
  read_csv(here(data_location,'exit.csv')) %>% select(playerId, gameId,human, workedWell, fair, chatUseful) %>% filter(!is.na(gameId))

>>>>

# TODO
- for less munging, put player role into round
- put players increment into record!

- Raise the stakes (game length / pay / bonus)

Next pilot 
- second page of instructions about bonus v base pay
- 40 trials (~15 minutes) aim for $3-4 bonus 
- can you have a get to know you at the beginning for 30-60 seconds? 
- switch to stag hunt? or other coord game (BoS)

- switch to BoS -- what are payoffs? (A,B; 0,0)

# Pre-process

@@

# Metrics
Paid $4 based on 20 minutes (including instructions, waiting, game, and end survey).

Welp, people definitely took the "click through" approach ...

@@

```{r}
pairs <- d.round_results %>% select(playerId,gameId) %>% unique()
d.players <- read_csv(here(data_location, 'players.csv')) %>% select(playerId=`_id`,data.bonus) %>% filter(!is.na(data.bonus)) %>% left_join(pairs) %>% arrange(gameId)

d.players
```

@@

```{r}
  comments <- read_csv(here(data_location,'exit.csv')) %>% select(playerId, gameId, human, workedWell, fair, chatUseful) %>% filter(!is.na(gameId)) %>% arrange(gameId)

comments %>% select(playerId, human, workedWell)

comments %>% select(playerId,fair)

comments %>% select(playerId, chatUseful)
